AGEAS: Automated Machine Learning based Genetic Featrue Extraction System

### 2022-10-03 docs/manuscript/main.tex
v0.0.1a9
guess I should leave liver fibrosis stuffs to pro

      After all pseudo-samples have been used to reconstruct psGRN, every psGRN can be represented as matrix comprising GRPs' PCC values and corresponding genes' expression values.
      The order of GRPs in each psGRN is also unified through adding GRPs included in other psGRNs with 0.0 PCC value.

@@

  From extracted TFs shown in Figure \ref{result_figs}(a), we hypothesize ISL1, PHOX2B, and ELF3 are regulating essential functions differentiating DA neurons from neural progenitors.
  Both ISL1 and PHOX2B were found related with DA phenotype in previous studies:
  ISL1 is essential for differentiation of prethalamic DA neurons\cite{isl1_da},
  and PHOX2B is connected with TH expression influencing DA neuron development and improving DA activity \cite{phox2_caudal_da, phox2_rat_da}
  Moreover, ELF3 was found to be neuronal precursor cell marker associated with neural stem cell development \cite{ELF3_precursor_marker}, consistent with it's high expression level in neuronal co-culture class.

  ASCL1, found as necessary factor regulating DA neurotransmitter selection by original research where we retrieved scRNA-Seq data\cite{ASCL1_dopaminergic_neuron_2021}, is also forming substantial regulon with extracted GRPs.

@@

  Esr1: estrogenic regulation for normal myocardial development was primarily via ER-alpha(Esr1)
  % (10.1016/j.mce.2013.11.011)
  % (http://dx.doi.org/10.1016/j.mce.2013.11.011)
  Cebpb: The Transcription Factor CEBP-beta Serves as a Master Regulator of physiologic Cardiac Hypertrophy
  % (Cell. 2010;143:1072–1083)
  % (Originally published4 Feb 2011https://doi.org/10.1161/RES.0b013e31820ff484Circulation Research. 2011;108:277–278)
  % https://doi.org/10.1016/j.mce.2014.03.007
  Sp1: upregulates the expression of GATA4 and atrial natriuretic peptide (ANP) in cardiomyoblast cells promote hypertrophy
  % https://doi.org/10.1142/S0192415X18500532 (2018).
  % Sp1 and Sp3 transcription factors are required for trans-activation of the human SERCA2 promoter in cardiomyocytes: Electrophysiology and Ca2+ handling
  % https://doi.org/10.1016/S0008-6363(03)00529-7, 10.1161/CIRCRESAHA.119.315862

@@

  Lhx2
  Osr1
  Ebf1

@@

  \vspace{\baselineskip}
  \noindent To demonstrate empirically the predictive capabilities... in vitro experiment Lhx2 repressing HSC activation...

>>>>

      After all pseudo-samples have been used to reconstruct psGRN, every psGRN can be represented as matrix comprising GRPs' PCC values.
      The order of GRPs in each psGRN is also unified through adding GRPs included in other psGRNs with 0.0 PCC value.

@@

  From extracted TFs shown in Figure \ref{result_figs}(b), we hypothesize ISL1, PHOX2B, and ELF3, referring to their correspond regulon sizes and expression changes, are regulating essential functions differentiating DA neurons from neural progenitors.
  Both ISL1 and PHOX2B were found related with DA phenotype in previous studies:
  ISL1 is essential for differentiation of prethalamic DA neurons\cite{isl1_da},
  and PHOX2B is connected with TH expression influencing DA neuron development and improving DA activity \cite{phox2_caudal_da, phox2_rat_da}
  Moreover, ELF3 was found to be neuronal precursor cell marker associated with neural stem cell development \cite{ELF3_precursor_marker}, consistent with it's high expression level in neuronal co-culture class.

  EBF1, which forms the largest regulon with extracted GRPs, was determined as key neuronal differentiation regulator in the ventral telencephalon, nature source of neuronal and glial cells \cite{ebf1_striatum, ebf1_cell_diff}.
  Furthermore, EBF1 plays important role in mesodiencephalic DA neuron migration. \cite{ebf1_migration}
  ASCL1, found as necessary factor regulating DA neurotransmitter selection by original research where we retrieved scRNA-Seq data\cite{ASCL1_dopaminergic_neuron_2021}, is also forming substantial regulon.
  % SOX2 and NR3C1 also have reports in neuronal differentiation...

@@

  Following same regulon size and expression change based analytical procedure, we primarily investigated three TFs shown in Figure \ref{result_figs}(c): Sp1, Esr1 ($ER\alpha$), and Cebpb.
  Previous studies demonstrated that Sp1 promotes CM hypertrophy \cite{sp1_hypertrophy} and maturation of electrophysiology and $Ca^{2+}$ handling \cite{Sp1_electrophysiologt, CM_mature}.
  % trans-activation of the SERCA2 promoter
  Esr1 was found modulating myocardial development for postnatal cardiac growth\cite{esr1_cm, esr1_cm_growth}, and Cebpb's role as repressor of CM growth and proliferation while preventing pathological CM hypertrophy also demonstrated by several studeis\cite{cebpb_1, cebpb_2}.

  Other TFs known playing important roles in CM maturation, such as Srf\cite{CM_mature, cebpb_1}, Nkx2-5\cite{cebpb_1, nkx25}, and Yap1\cite{CM_mature, yap1}, are also forming sizeable regulons in GRN atlas returned by \emph{AGEAS} .

@@

  Within TFs shown in Figure \ref{result_figs}(d), we suppose Lhx2, Osr1, and Ebf1 are regulating phenotypes clearly differentiating HSCs from PFs considering their correspond TF regulon sizes and expression changes.

  Osr1 fibrogenic regulation

  Ebf1 ...

  Lhx2 halt quiescent HSCs

  Furthermore, Mef2c forming top TF regulon is main regulator of collagen expression...

@@

  \vspace{\baselineskip}
  \noindent To demonstrate empirically the predictive capabilities...
  Since Lhx2 has largest expression change while favoring in HSCs...
  but not directly regulating fibrogenic genes as Mef2c does...
  in vitro experiment overexpression of Lhx2 repressing HSC activation...
